### 2019-12-27 thesis/mini/abstract.tex
thesis version printed

Continuous integration produces detailed logs about the status and results of the various tools involved in the build.
These build logs are a valuable data source for developers and researchers to inspect test results, the duration of build steps and understand the cause of a build failure.
However, build logs are very verbose, at best semi-structured and their structure differs highly between projects.
This makes it hard to process and analyze them.
In this thesis, we evaluate and compare three different techniques that aim to retrieve specified log parts (chunks) from a build log, namely program synthesis by example, textual similarity and search keywords.
We conduct an empirical study by comparing these techniques on our manually labeled \emph{LogChunks} data set of 797 Travis CI logs from 80 GitHub projects and a broad range of 29 programming languages.
Our findings show that none of the three techniques in general outperforms the others.
We discuss under which circumstances each technique performs best and provide a recommendation on when developers or researchers should use which technique.

>>>>

Continuous integration produces detailed logs about the status and results of the various tools involved in the build.
These build logs are a valuable data source for developers and researchers to inspect test results, to check the duration of build steps and to understand the cause of a build failure.
However, build logs are very verbose, at best semi-structured and their structure differs highly between projects.
This makes it hard to process and analyze them.
In this thesis, we evaluate and compare three different techniques that aim to retrieve specified log parts (chunks) from a build log, namely program synthesis by example, textual similarity and search keywords.
We conduct an empirical study by comparing these techniques on our manually labeled \emph{LogChunks} data set of 797 Travis CI build logs from a broad range of 80 projects.
Our findings show that none of the three techniques in general outperforms the others.
We discuss under which circumstances each technique performs best and provide a recommendation on when developers or researchers should use which technique.

### 2019-12-27 thesis/mini/acknowledgments.tex
thesis version printed

\vspace{1cm}
\noindent
I would like to thank Dr. Moritz Beller for his great support, his detailed feedback and his invaluable teaching how to do research.
I could not have imagined a better advisor for my master's thesis.

\noindent
Furthermore, I would like to thank Prof. Annibale Panichella for his helpful feedback and teaching me the proper vocabulary to describe my work.

\noindent
I want to pay my special regards to Prof. Alexander Pretschner for his critical questions, leading me to continuously challenge my evaluation and the problems my work addresses.
I would like to thank Prof. Alexander Knapp for his sharp eyes for formulas and our reassuring conversations.

>>>>

\vspace{1cm}
\noindent
I would like to thank Dr.\ Moritz Beller for his great support, his detailed feedback and his invaluable teaching on how to do research.
I could not have imagined a better advisor for my master's thesis.

\noindent
Furthermore, I would like to thank Prof.\ Annibale Panichella for his helpful feedback and teaching me the proper vocabulary to describe my work.

\noindent
I want to pay my special regards to Prof.\ Alexander Pretschner for his critical questions, leading me to continuously challenge my evaluation and the problems my work addresses.
I would like to thank Prof.\ Alexander Knapp for his sharp eyes for formulas and our reassuring conversations.

### 2019-12-27 thesis/txt/1-related-work.tex
thesis version printed

\chapter{Background and Related Work}
\label{sec:rw}
This chapter presents various research works adjacent or foundational to our work.
The first section presents existing work in the field of continuous integration (CI) and showcases how researchers analyze build logs.
In the second section we describe the existing methods which are the foundation for the chunk retrieval we investigate.
% moritz: nice formulation :)

\section{Continuous Integration and Build Logs}
We describe existing studies about CI to show that CI is a relevant topic within the software engineering research community.
We explain how researchers gather information about CI usage in software projects through build log analysis and why the chunk retrieval techniques we investigate simplifys their data collection.
This section moves on to past works about augmenting build logs to make it easier for developers to inspect them.
The presented approaches are related to and can benefit from the techniques we analyze in this thesis.
Further, we classify build logs as semi-structured data and differentiate our work from system log analysis.
% CI describes the practice of integrating, building and testing source code changes often and fast.
% The tools involved in a CI build communicate their progress and status through a combined build log.
% In Section~\ref{sec:bl-characteristics}, we describe CI builds and how

@@

\paragraph{Data Sets Powering CI Research}
The works presented in this section are based on either developer surveys or data setsa containing build metadata or build logs.
Seo et al.~\cite{seo2014programmers} and Vassallo et al.~\cite{vassallo2017a-tale} based their analyses on sets of build logs collected from industry partners.
Beller et al.~\cite{beller2017travistorrent} created the \emph{TravisTorrent} data set providing access to build metadata from more than 1,000 projects from Travis CI~\cite{travisci2019webpage}.
\emph{TravisTorrent} was the basis for several of the works mentioned in this section~\cite{rausch2017empirical,zampetti2017open,vassallo2017a-tale,beller2017oops}.
Ghaleb et al.~\cite{ghaleb2019studying} aim to identify noise in build breakage data.
They classify build failures from \emph{TravisTorrent} according to whether they were caused by an environmental failure or caused by a developer change.
They also identify cascading build failures created by existing unfixed errors and allowed failures, whose results were later labeled by developers to be ignored.
About half of the failed builds in \emph{TravisTorrent} fall into at least one of these categories.
When regarded as noise they considerably impact observations reported by other works modeling build breakages.

@@

\subsection{Program Synthesis by Example}
\label{sec:rw-prose}
Programming by Example enables end users to automate repetitive tasks.
The user provides examples for the input and the corresponding output and a synthesis algorithm tries to create the program intended by the user.
This section introduces the theoretical foundations of the program synthesis algorithm of the \emph{Program Synthesis using Examples} (PROSE) framework~\cite{prose2019webpage}.
The PROSE framework is developed by Microsoft Research.
Next, this section presents the FlashExtract DSL, which defines text extraction tasks within PROSE and is the basis for the implementation of our chunk retrieval technique PBE\@.
Finally, we cover additional applications and extensions of the PROSE program synthesis and alternative research on generating regular expressions from examples.

>>>>

\chapter{Background and Related Work}
\label{sec:rw}
This chapter presents various research works adjacent or foundational to our work.
The first section presents existing work in the field of continuous integration (CI) and showcases how researchers analyze build logs.
In the second section we describe the existing methods which are the foundation for the chunk retrieval techniques we investigate.
% moritz: nice formulation :)

\section{Continuous Integration and Build Logs}
We describe existing studies about CI to show that CI is a relevant topic within the software engineering research community.
We explain how researchers gather information about CI usage in software projects through build log analysis and why the chunk retrieval techniques we investigate simplifies their data collection.
This section moves on to past works about augmenting build logs to make it easier for developers to inspect them.
The presented approaches are related to and can benefit from the techniques we analyze in this thesis.
Further, we classify build logs as semi-structured data and differentiate our work from system log analysis.
% CI describes the practice of integrating, building and testing source code changes often and fast.
% The tools involved in a CI build communicate their progress and status through a combined build log.
% In Section~\ref{sec:bl-characteristics}, we describe CI builds and how

@@

\paragraph{Data Sets Powering CI Research}
The works presented in this section are based on either developer surveys or data sets containing build metadata or build logs.
Seo et al.~\cite{seo2014programmers} and Vassallo et al.~\cite{vassallo2017a-tale} based their analyses on sets of build logs collected from industry partners.
Beller et al.~\cite{beller2017travistorrent} created the \emph{TravisTorrent} data set providing access to build metadata from more than 1,000 projects from Travis CI~\cite{travisci2019webpage}.
\emph{TravisTorrent} was the basis for several of the works mentioned in this section~\cite{rausch2017empirical,zampetti2017open,vassallo2017a-tale,beller2017oops}.
Ghaleb et al.~\cite{ghaleb2019studying} aim to identify noise in build breakage data.
They classify build failures from \emph{TravisTorrent} according to whether they were caused by an environmental failure or caused by a developer change.
They also identify cascading build failures created by existing unfixed errors and allowed failures, whose results were later labeled by developers to be ignored.
About half of the failed builds in \emph{TravisTorrent} fall into at least one of these categories.
When regarded as noise they considerably impact observations reported by other works modeling build breakages.

@@

\subsection{Program Synthesis by Example}
\label{sec:rw-prose}
Programming by Example enables end users to automate repetitive tasks.
The user provides examples for the input and the corresponding output and a synthesis algorithm tries to create the program intended by the user.
This section introduces the theoretical foundations of the program synthesis algorithm of the \emph{PROgram Synthesis using Examples} (PROSE) framework~\cite{prose2019webpage}.
The PROSE framework is developed by Microsoft Research.
Next, this section presents the FlashExtract DSL, which defines text extraction tasks within PROSE and is the basis for the implementation of our chunk retrieval technique PBE\@.
Finally, we cover additional applications and extensions of the PROSE program synthesis and alternative research on generating regular expressions from examples.

### 2019-12-27 thesis/txt/6-discussion.tex
thesis version printed

\subsection{Keyword Search (KWS)}
\paragraph{Configuration and Input}
KWS has a higher recall than the two other techniques for multiple structural categories present in the training and test examples.\@.
This makes KWS a good technique if there is little prior knowledge on how the targeted log chunk is represented in the build log to be analyzed.
For the example of extracting the reason the build failed, KWS is best suited if a build can fail in various steps logged by different tools and no pre-categorization of where the build failed is available.

>>>>

\subsection{Keyword Search (KWS)}
\paragraph{Configuration and Input}
KWS has a higher recall than the two other techniques for multiple structural categories present in the training and test examples.
This makes KWS a good technique if there is little prior knowledge on how the targeted log chunk is represented in the build log to be analyzed.
For the example of extracting the reason the build failed, KWS is best suited if a build can fail in various steps logged by different tools and no pre-categorization of where the build failed is available.
